Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-07-05 results.tex
cleaning

We also note that the overall distribution of PGA values shown in Fig.~\ref{fig:pgaavgs}c are the ones that best agree with the recent study by \citet{Khodaverdian_2016_BSSA}. These estimates also agree, on average, with other previous studies. For the north-west seismic regions of Azerbaijan and Zagros, for instance, \citet{Tavakoli1999} predicts maximum mean PGA values of 0.45 g near the North Tabriz Fault and the North Tehran Fault zones, and 0.4 g around the city of Urmia, where we find equivalent values to be between 0.4 and 0.6 g, and about 0.35 g, respectively. The results from \citet{Vafaie2011} for the city of Tabriz, on the other hand, are slightly higher than the averages shown in Fig.~\ref{fig:pgaavgs}c and are closer to those we present in Fig.~\ref{fig:pga}b, which are in the order of 0.8 g and 0.6 for the models 2U5.5 and 10U5.5. In the north-central region of Alborz, \citet{Ghodrati2003} and \citet{Boostan2015} predict PGA values of the order 0.27--0.46 g and 0.42--0.48 for Tehran, where we found equivalent results to be between 0.3 and 0.45 g. Similarly, \citet{Abdi2013} reports expected PGA values in the vicinity of Karaj and Tehran to be on the order of 0.3 g. Results from \citet{Ghodrati2008} for the Gilan province around the city of Rasht are also of the same order of those we show in Figs.~\ref{fig:pga} and \ref{fig:pgaavgs}c. Finally, in for the Kopeh Dagh region, and in particular, for the city of Bojnurd in the nort-east province of Khorasan, \citet{Rahgozar2012} reports expected PGA values for return periods of 475 and 2475 years in range of 0.15--0.22 g and 0.28--0.49 g, respectively, where for magnitudes exceeding $M_w$ 6.5 we found equivalent values to be in the order of 0.2--0.4 and 0.4--0.6 g.

@@

>>>>

We also note that the overall distribution of PGA values shown in Fig.~\ref{fig:pgaavgs}c are the ones that best agree with the recent study by \citet{Khodaverdian_2016_BSSA}. These estimates also agree, on average, with other previous studies. For the north-west seismic regions of Azerbaijan and Zagros, for instance, \citet{Tavakoli1999} predicts maximum mean PGA values of 0.45 g near the North Tabriz Fault and the North Tehran Fault zones, and 0.4 g around the city of Urmia, where we find equivalent values to be between 0.4 and 0.6 g, and about 0.35 g, respectively. The results from \citet{Vafaie2011} for the city of Tabriz, on the other hand, are slightly higher than the averages shown in Fig.~\ref{fig:pgaavgs}c and are closer to those we present in Fig.~\ref{fig:pga}b, which are in the order of 0.8 g and 0.6 for the models 2U5.5 and 10U5.5. In the north-central region of Alborz, \citet{Ghodrati2003} and \citet{Boostan2015} predict PGA values of the order 0.27--0.46 g and 0.42--0.48 for Tehran, where we found equivalent results to be between 0.3 and 0.45 g. Similarly, \citet{Abdi2013} reports expected PGA values in the vicinity of Karaj and Tehran to be on the order of 0.3 g. Results from \citet{Ghodrati2008} for the Gilan province around the city of Rasht are also of the same order of those we show in Figs.~\ref{fig:pga} and \ref{fig:pgaavgs}c. Finally, in for the Kopeh Dagh region, and in particular, for the city of Bojnurd in the nort-east province of Khorasan, \citet{Rahgozar2012} reports expected PGA values for return periods of 475 and 2475 years in range of 0.15--0.22 g and 0.28--0.49 g, respectively, where for magnitudes exceeding $M_w$ 6.5 we found equivalent values to be in the order of 0.2--0.4 and 0.4--0.6 g. Table \ref{tab:pga} shows a condensed version of these comparisons between our results and those of previous studies for different points of interest (cities) in northern Iran.

\begin{table}[t]
    \centering
    \caption{Comparison of expected PGA values for selected cities in northern Iran between results obtained in this study and those of others. For reference, the following codes are used. Va11: \citet{Vafaie2011}, Gh08: \citet{Ghodrati2008}, Bo15: \citet{Boostan2015}, Gh03: \citet{Ghodrati2003}, Ab14: \citet{Abdollahzadeh2014a}, Ra12: \citet{Rahgozar2012}, Ad13 \citet{Abdi2013}.}
    \begin{tabular}{l}
        \hline
        Cities      \\
        \hline
        Urumieh     \\
        Tabriz      \\
        Ardabil     \\
        Zanjan      \\
        Manjil      \\
        Rasht       \\
        Qazvin      \\
        Karaj       \\
        Tehran      \\
        Sari        \\
        Semnan      \\
        Gorgan      \\
        Bojnurd     \\
        Mashhad     \\
        \hline
    \end{tabular}
    \label{tab:pga} 
\end{table}

@@

% The areas of large probabilistic ground motions clearly coincide with zones with a large number of events of magnitude 3.0 and larger. In this study we used two models for seismic hazard calculation, including $M_w>5$ and $M_w>4.5$. $M_w$ is the minimum magnitude that can affect the engineering site.

% In the probabilistic seismic hazard analysis increasing minimum magnitude will decrease the mean rate of earthquake occurrence ($\nu=exp(\alpha - \beta M_0)$), and also increase the value for the probability density function in the initial magnitudes. In a simple source the difference between different models specially in higher pga levels is negligible. However, in this study where we consider each event as a seismic source with different $\alpha$ and $\beta$ value, the results are considerably different. According to our results the reduction of the mean rate of earthquake occurrence has considerable effect on the results.
